Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\midd}{{\mbox{\wesa{middle}}}}
\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\minus}{\texttt{-}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}

@@

\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any random variable~$X:\Omega\rightarrow\mathbb{R}$. $\bar{\mu}$
is convex if and only if

@@

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectrum decomposition is given by
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
is given by
\begin{equation}
\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\Tr\left(\rho P_{i}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .
\end{equation}

>>>>

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\midd}{{\mbox{\wesa{middle}}}}
\usepackage[braket,qm]{qcircuit}
\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\minus}{\texttt{-}}

@@

\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
is convex if and only if

@@

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectrum decomposition is given by
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\rho}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Given the same observable with an extra condition~$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$,
we can combine equation~(\ref{eq:interval-expectation}) and (\ref{eq:quantum-expectation})
to define the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(\sum_{j\ge i}P_{j}\right)-l\left(\sum_{j\ge i+1}P_{j}\right),r\left(\sum_{j\ge i}P_{j}\right)-r\left(\sum_{j\ge i+1}P_{j}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}
